When easy is not preferred: A discounting paradigm to assess load-independent task preference

### 2023-02-23 06_Paper/COG-ED/Stage 2/Manuscript.Rmd
wrote SCA results

Consequently, we had to adapt the multi level model to incorporate this non-linear trend.
To apply the contrast to the *n*-back levels, we had to turn the variables into a factor, with two consequences:
Centered variables cannot be turned into factors, so we entered the variables in their raw form, and factors cannot be used as random slopes, so the model is now defined as:
$$
SV \sim level\ + d' + median RT + (1|subject)
$$
This means that the intercept still varies between subjects, but there are no random slopes anymore.
To provide more than one observation per factor level, we used the two rounds per level per subject, rather than levels per subject.
The ICC of the null model indicated that there is a correlation of `r $r=round(model0_h2b_ICC, digits = 3)$` between the SVs of a subject, i.e. that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs can be explained by differences between participants.
We did not use an optimization algorithm to improve the fit of the random intercept model.
A total of `r nrow(excl_cases_h2b$subject)` data points from `r length(excl_cases_h2b)` were excluded, because the residuals exceeded 3 SD above the mean.
The results of the final model are displayed in Table\ \@ref(tab:H2b-results)

@@

To investigate the dependency of the model results on the RT preprocessing, we conducted a specification curve analysis.

@@

```{r sca-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Results of the multi level model for each of the 63 preprocessing pipelines. The lower panel indicates the type of preprocessing, the middle panel shows the p-value of the full model, and the upper panel the beta coefficient as a line and its standard deviation as a vertical box. The colourbar indicates the BF10.", fig.pos="H"}

@@

>>>>

Consequently, we had to adapt the multi level model to incorporate this non-linear trend.
To apply the contrast to the *n*-back levels, we had to turn the variables into a factor, with two consequences:
Centered variables cannot be turned into factors, so we entered the variables in their raw form, and factors cannot be used as random slopes, so the model is now defined as:
$$
SV \sim level\ + d' + median RT + (1|subject)
$$
This means that the intercept still varies between subjects, but there are no random slopes anymore.
To provide more than one observation per factor level, we used the two rounds per level per subject, rather than levels per subject.
The ICC of the null model indicated that there is a correlation of `r $r=round(model0_h2b_ICC, digits = 3)$` between the SVs of a subject, i.e. that `r paste0(formatC(model0_h2b_ICC * 100, format = "f", digits = 2), "%")` of variance in SVs can be explained by differences between participants.
We did not use an optimization algorithm to improve the fit of the random intercept model.
A total of `r nrow(excl_cases_h2b$subject)` data points from `r length(excl_cases_h2b)` were excluded, because the residuals exceeded 3 SD above the mean.
The results of the final model are displayed in Table\ \@ref(tab:H2b-results).

@@

To investigate the dependency of the model results on the RT preprocessing, we conducted a specification curve analysis (Figure\ \@ref(fig:sca-plot)).

@@

```{r sca-plot, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Results of the multi level model for each of the 63 preprocessing pipelines. The lower panel indicates the type of preprocessing, the upper panel shows the beta coefficient of each predictor and its p-value. The colourbar indicates the BF10. The pipelines are sorted in descending order of the magnitude of the n-back level beta.", fig.pos="H"}

@@

Regardless of the preprocessing pipeline, *n*-back level and *d'* were significant predictors of SVs, and had stable effect estimates across all pipelines.
The only pipelines, in which the median RT was a significant predictor of SVs, were the three pipelines with the highest Bayes Factors and the largest effect of *n*-back level.
These three pipelines contain data that has been inverse transformed across subjects but within conditions, i.e. within the round of an *n*-back level.
The two "spikes" in the beta of the median RT in Figure\ \@ref(fig:sca-plot) are from the other two pipelines that used inverse transformation.
